Post MCMCglmm analyses

### 2021-04-28 Analysis/06-post_mcmcglmm_analyses.Rmd
Update 06-post_mcmcglmm_analyses.Rmd

```{r, eval = FALSE}
## Global per tip analyses
tip_results_global <- analyses.tip(data = morphdat, axes = uncentered_major_axes$phylogeny)

## Plot results
plot.analyses.tip(tip_results_global, cols = colour_vector, group = split(rownames(morphdat), f = morphdat$clade)))
```

>>>>

```{r}
## Global per tip analyses
tip_results_global <- analyses.tip(data = morphdat[, c(1:3)], axes = uncentered_major_axes$animal)

## Plot results
plot.analyses.tip(tip_results_global, cols = colour_vector, group = split(rownames(morphdat), f = morphdat$clade))
```
